Network Configuration Synthesis with Abstract Topologies

### 2016-11-04 paper/abstraction/paper.tex
stashing changes
rework inference rules
add local and global pod inference rules

\newcommand{\inference}[4]{
    \node[draw, anchor=west] at (#1 + .4, 1.25) {#3};
    \node at (#1 + .34, .6) {$e_1$};
    \node at (#1 + .34, 1.9) {$e_2$};
    \node at (#1, -.8) {#2};
    \node at (#1, 3.3) {#4};
    \draw [] (#1, 2.5) circle [radius=0.45] node {$n$};
    \draw [] (#1, 0) circle [radius=0.45] node {$m$};
    \draw [] (#1, .45) -- (#1, 2.05);
}

\begin{figure*}[t!]
  \begin{minipage}[t]{.5\linewidth}%
  \begin{tikzpicture}
    \inference{0}{L$(j,k)$}{$\vDash e_1 > 0$}{S$(min(j*k,e_1),1)$}
    \inference{5}{A$(j,k)$}{$e_2 > 0$}{A$(1,min(j,e2))$}
    \inference{10}{L$(j,k)$}{$e_1=n$}{A$(min(j*k,n),1)$}
    \inference{15}{L$(j,k)$}{$e_1=n$}{A$(1,j)$}
  \end{tikzpicture}
  \end{minipage}

  %
  \vspace*{3em}
  %
  \begin{minipage}[t]{.5\linewidth}%
  \begin{tikzpicture}
    \inference{0}{L$(j,k)$}{$e_1 > 0$, $e_2 > 0$}{S$(min(j*k,n-\dfrac{(m-j)*e_1}{e_2}),1)$}
    \inference{10}{L$(j,k)$ ~~~ L$(j- m ~\text{mod}~ \big(\dfrac{n}{e_1}\big),1)$}{$e_1 > 0$, $e_2 > 0$}{}
  \end{tikzpicture}
  \end{minipage}

  \vspace*{1em}
  \hrule
  \vspace*{1em}
  \caption{Abstract k-disjoint path analysis inference rules.}
  \label{fig:inference-rules}
  %\vspace{-1em}
\end{figure*}

@@

In order to learn information about disjoint paths between routers, we develop a series of sound inference rules for facts of the above form. Figure~\ref{fig:inference-rules} shows each of the inference rules.

@@

\begin{figure}
  \subcaptionbox{Datacenter}
    {\includegraphics[width=.49\columnwidth]{figures/Fattree-time.png}}
  \subcaptionbox{Backbone}
    {\includegraphics[width=.49\columnwidth]{figures/backbone-time.png}} \\
  \caption{Concrete vs. Abstract Compilation Time. \label{fig:compilation-times}}
  \vspace{-1em}
\end{figure}

@@

\begin{figure*}[t]\small
  \begin{minipage}[t]{.45\linewidth}
  \hdr{Syntax}{}
  \vspace*{-1\baselineskip}
  %
  \[ \begin{array}{rclr}
    \hline%

>>>>

\newcommand{\inference}[7]{
    \node[draw, anchor=west] at (#1 + .4, 1.25) {#3};
    \node[anchor=east] at (#1 - .4, 1.25) {\textbf{#5}};
    \node at (#1 + .34, .6) {#6};
    \node at (#1 + .34, 1.9) {#7};
    \node at (#1, -.8) {#2};
    \node at (#1, 3.3) {#4};
    \draw [] (#1, 2.5) circle [radius=0.45] node {$n$};
    \draw [] (#1, 0) circle [radius=0.45] node {$m$};
    \draw [->] (#1, .45) -- (#1, 2.05);
}

\newcommand{\inferencenobox}[7]{
    \node[anchor=west] at (#1 + .4, 1.25) {#3};
    \node[anchor=east] at (#1 - .4, 1.25) {\textbf{#5}};
    \node at (#1 + .34, .6) {#6};
    \node at (#1 + .34, 1.9) {#7};
    \node at (#1, -.8) {#2};
    \node at (#1, 3.3) {#4};
    \draw [] (#1, 2.5 - .2) circle [radius=0.45] node {$n$};
    \draw [] (#1, .2) circle [radius=0.45] node {$m$};
    \draw [->] (#1, .2 + .45) -- (#1, 2.5 - .45 - .2);
}

\newcommand{\inferencetwo}[1]{
    \node[draw, anchor=west] at (#1 + 2, 1.25) {$e_i > 0$};
    \node[anchor=east] at (#1 - .4, 1.25) {\textbf{I-striping}};
    \node at (#1 - 1 - .11, .6) {$e_1$};
    \node at (#1 + .11, 1.9) {$e_2$};
    \node at (#1 + 2 + .11, .6) {$e_3$};
    \node at (#1 + .11 + .8, 1.9) {$e_4$};
    \node at (#1 - 1, -.8) {L$(j,k)$};
    \node at (#1 +. 5, 3.3) {S$(min(j*k,g),1)$};
    \node at (#1 + 2, -.8) {L$\big( min(j, g *\frac{e_4}{e_3}),1\big)$};
    \node at (#1, 3.3) {};
    \draw [] (#1 + .5, 2.5) circle [radius=0.45] node {$n$};
    \draw [] (#1 - 1, 0) circle [radius=0.45] node {$m$};
    \draw [] (#1 + 2, 0) circle [radius=0.45] node {$o$};
    \draw [->] (#1 - 1, .45) -- (#1 + .5, 2.05);
    \draw [<-] (#1 + 2, .45) -- (#1 + .5, 2.05);
}

\newcommand{\inferencelocal}[1]{
    \inferencenobox{#1}{L$_1(j,k)$}{}{L$_2(j',k')$}{I-local}{}{}
    \inferencenobox{#1+3}{$\ldots$ L$_P$ L$_1(j,k)$}{}{$\ldots$ L$_P$ L$_2(j',k')$}{}{}{}
    \node[anchor=east] at (#1 + 3 - .6, 2.6) {P};
    \draw[dashed] (#1+2 - .2, -.44) rectangle (#1+3+1 + .1, 2.95);
}

\newcommand{\inferenceglobal}[1]{
    \inferencenobox{#1}{L$_1(j,k)$}{}{L$_2(j',k')$}{I-global}{}{}
    \inferencenobox{#1+3}{$\ldots$ L$_P$ L$_1(j,k)$}{}{$\ldots$ A$_P$ L$_2(j',k')$}{}{}{}  
    \node[anchor=east] at (#1 + 3 - .6, .54) {P};  
    \node[anchor=east] at (#1 + 3 - .6, 2.6) {Q};
    \draw[dashed] (#1+2 - .2, -.44) rectangle (#1+3+1 + .1, .9);
    \draw[dashed] (#1+2 - .2, 1.6) rectangle (#1+3+1 + .1, 2.95);
}

\begin{figure*}[t!]
  \begin{minipage}[t]{\linewidth}%
  \begin{tikzpicture}
    \inference{0}{L$(j,k)$}{$e_1 > 0$}{S$(min(j*k,e_1),1)$}{I-out1}{$e_1$}{$e_2$}
    \inference{4.5}{A$(j,k)$}{$e_2 > 0$}{A$(1,min(j,e2))$}{I-out2}{$e_1$}{$e_2$}
    \inference{9}{L$(j,k)$}{$e_1=n$}{A$(min(j*k,n),1)$}{I-mesh1}{$e_1$}{$e_2$}
    \inference{13.5}{L$(j,k)$}{$e_1=n$}{A$(1,j)$}{I-mesh2}{$e_1$}{$e_2$}
  \end{tikzpicture}
  \end{minipage}

  \vspace*{1em}
  \begin{minipage}[t]{\linewidth}%
  \begin{tikzpicture}
    % \inference{0}{L$(j,k)$}{$e_i > 0$}{S$(min(j*k,g),1)$}{I-out3}{$e_1$}{$e_2$}
    \inferencetwo{0}
    \node[anchor=west] at (2,2.4) {where $g=n-\dfrac{(m-j)*e_1}{e_2}$};
    \inference{11}{L$(j,k)$}{$bisec(X)$}{A$(1,min(k,X))$}{I-bisec}{}{}
  \end{tikzpicture}
  \end{minipage}

  \vspace*{1em}
  \begin{minipage}[t]{\linewidth}%
  \begin{tikzpicture}
    \inferencelocal{0}
    \inferenceglobal{10}
  \end{tikzpicture}
  \end{minipage}

  \hrule
  \vspace*{1em}
  \caption{Abstract k-disjoint path analysis inference rules. \ryan{added bisec idea a possibility, we can remove this}}
  \label{fig:inference-rules}
  %\vspace{-1em}
\end{figure*}

@@

\subsection{Inference rules}

In order to learn information about disjoint paths between routers, we develop a series of sound inference rules for facts of this form. Figure~\ref{fig:inference-rules} shows each of the inference rules.

@@

\begin{figure}[t!]
  \subcaptionbox{Datacenter}
    {\includegraphics[width=.49\columnwidth]{figures/Fattree-time.png}}
  \subcaptionbox{Backbone}
    {\includegraphics[width=.49\columnwidth]{figures/backbone-time.png}} \\
  \caption{Concrete vs. Abstract Compilation Time. \label{fig:compilation-times}}
  \vspace{-1em}
\end{figure}

@@

\begin{figure*}[t!]\small
  \begin{minipage}[t]{.45\linewidth}
  \hdr{Syntax}{}
  \vspace*{-1\baselineskip}
  %
  \[ \begin{array}{rclr}
    \hline%
